How demand pattern identification and multicriteria ABC classification can guide management decisions

### 2024-01-17 manuscript/FCPCOM/manuscript.tex
updating introduction

Decades of experience in applying the philosophy of lean production eventually popularized the famous saying: "stock is a necessary evil" \citep{Younkin2021}. On the one hand the stock of raw materil, and finished and semi-finished goods serves to reduce the delivery time for the customer and ensure that possible failures in the process do not generate greater influence on production efficiency as well as delays in deliveries, on the other hand the stock usually represents a high cost, allocation of spaces that could be used for other purposes, possibilities of loss and depreciation, in addition to hiding process failures \citep{Shingo1996}. Briefly, it is safe to say that stock is unavoidable and must be kept up with in suitable amount, and the well-organized management of raw materials and supplies, semi-finished goods and finished goods is nominated Inventory Control \citep{Nirmala2022}.

>>>>

Decades of experience in applying the philosophy of lean production eventually popularized the famous saying: "stock is a necessary evil" \citep{Younkin2021}. On the one hand the stock of raw material, and finished and semi-finished goods serves to reduce the delivery time for the customer and ensure that possible failures in the process do not generate greater influence on production efficiency as well as delays in deliveries, on the other hand the stock usually represents a high cost, allocation of spaces that could be used for other purposes, possibilities of loss and depreciation, in addition to hiding process failures \citep{Shingo1996}. Briefly, it is safe to say that stock is unavoidable and must be kept up with in suitable amount, and the well-organized management of raw materials and supplies, semi-finished goods and finished goods is nominated Inventory Control \citep{Nirmala2022}.

As this topic is of utmost importance for companies, the scientific literature presents a large number of works proposing different techniques for Inventory Control (\emph{e.g.} incluir referências sobre trabalhos propondo novas técnicas de controle de inventário) and it is a unanimous conclusion that a multicriteria classification is an essential technique when inventory control involves a high quantity of different goods (incluir referências que dão suporte à frase), which is usually what happens in practice.
